GeoSPARQL 1.1: an almost decadal update to the most important geospatial LOD standard

### 2021-04-21 manuscript.tex
BibTek improvements

\institute{
    {
    %SURROUND Australia Pty Ltd., Australia \&\\
    Australian National University, Australia\\
    \email{nicholas.car@surroundaustralia.com}\\
    %\url{https://surroundaustralia.com}
    }
    \and
    {
        Mainz University Of Applied Sciences, Germany\\
        \email{timo.homburg@hs-mainz.de}
    }
    % \and 
    % {
    %     Commonwealth Scientific \& Industrial Research Organisation, Australia\\
    %     \email{simon.cox@csiro.au}
    % }
}

@@

\begin{abstract}
In 2012 the Open Geospatial Consortium published GeoSPARQL 
defining ``SPARQL extension functions'', ``RIF rules'', ``an RDF/OWL ontology for [spatial] information'' and supporting vocabularies.\\

>>>>

\institute{
    {
    SURROUND Australia Pty Ltd., Australia \&\\
    Australian National University, Australia\\
    \email{nicholas.car@surroundaustralia.com}\\
    }
    \and
    {
        Mainz University Of Applied Sciences, Germany\\
        \email{timo.homburg@hs-mainz.de}
    }
}

@@

\begin{abstract}
In 2012 the Open Geospatial Consortium published GeoSPARQL 
defining ``SPARQL extension functions'', ``RIF rules'' and ``an RDF/OWL ontology for [spatial] information''.\\
